\chapter{Conclusion}
\label{chap:conc}

The final product has turned out somewhat functional. it is able to provide suggestions based on users preferences and allows for easily obtained information about nearby stores and retailers. The problem statement described in \ref{sec:probstate} has in the clearest meaning been solved as the application is able to provide suggestions based on the preferences set by the specific user. It is however not ideal that the only preference to set at this given moment is monetary. The application could be greatly improved by having support for more preferences with more diversity so the target group could be broadened. We have as mentioned made it possible for each user to determine what the ideal radius for shopping is for them - this is perfect for fitting all target groups when it comes to means of transportation, whether by car, walking or other.

It should be noted that while serving recommendations are completely possible, the final product suffers greatly from a lack of data. At this point there are no available recipes unless entered manually, ingredients only from offers and statistics, and this makes it hard to actually make good recommendations.
Furthermore, we wanted to tag recipes to provide a form of meta-data that would improve the recommendation system, but again, this kind of information proved difficult to obtain without entering it manually.

The server has been developed with performance in mind. We have intentionally created some suboptimal spacial entities with the purpose of making certain queries faster. These queries are generally the ones used by the application, meaning that these queries are likely to be run often. The server does however spend some time making the calculations depending on how many recipes are in the database. The database was made accessible through a REST API, which was found to work very well. It was easy to access from the application, and also great at abstracting the database away. From the server side, extensive error handling is provided, meaning that if something should go wrong, the backend can recover, and will provide proper error messages for the application to deal with. The application is however responsible for handling cases where something goes wrong, but was not implemented in time. This makes the clients communication naive, and prone to fail.

The application is unfinished although runnable. It could most definitely use some polishing and new graphics, as the graphics currently used are purely android studio sprites. There are both unfinished components, visuals and elements that needs refinement. It is however able to provide an intuitive way of getting recommendations through ones own preferences, along with browsing the contents of a recipe. The goal of making it user-friendly, feature rich and stable was mostly met. Features are limited given the limited project period, but extensive enough to provide a somewhat useful application. A lot of thought has gone into the usability of the application, and as result it feels easy to use. It is however not stable, as a faulty attempt to communicate with the server could crash the application in its current state.

\input{Content/Conclusion/evaluation}
\input{Content/Conclusion/futurework}
